Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-01 edubots_surveys.Rnw
partially fixes population adding both surveys

survey.student.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
@

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<age,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<sector, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/sector.pdf}
    \end{minipage}

    \vspace{0.5mm}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<experience,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
        \centering
<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.2>>=
ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}
%
\begin{figure}[h!tbp]
\begin{center}
<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
library(forcats)
survey.student.interaction %>%
    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
        \centering
<<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
    \end{minipage}
\end{center}
    \caption{Synchronous or asynchronous interaction.}
\label{figure:chatbots_synch}
\end{figure}

>>>>

survey.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
survey.interaction %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freqInteraction.Age
survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience
survey.interaction %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
@

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.45\textwidth}
        \centering
<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Gender$source<-rep("survey1")
freqInteraction.Gender$source<-rep("survey2")
freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.45\textwidth}
        \centering
<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Age$source<-rep("survey1")
freqInteraction.Age$source<-rep("survey2")
freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
freqbinded.Age$source <- factor(freqbinded.Age$source) 
ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \vspace{0.5mm}
    \begin{minipage}[t]{0.5\textwidth}
        \centering
<<experience, echo=FALSE, fig.width=4.5, fig.height=2.5>>=
#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Experience$source<-rep("survey1")
freqInteraction.Experience$source<-rep("survey2")
freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/sector.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.4\textwidth}
        \centering
<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
#freq.Sector$source<-rep("survey1")
#freqInteraction.Sector$source<-rep("survey2")
#freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
#freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
#ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{\textwidth}
        \centering
<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.5>>=
#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Discipline$source<-rep("survey1")
freqInteraction.Discipline$source<-rep("survey2")
freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}

\begin{figure}[h!tbp]
\begin{center}
<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
library(forcats)
survey.interaction %>%
    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
        \centering
<<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
    \end{minipage}
\end{center}
    \caption{Synchronous or asynchronous interaction.}
\label{figure:chatbots_synch}
\end{figure}
